Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
write section 4b except the results

\usepackage{cleveref}
\usepackage{color}

@@

To show the potential benefit of automatic reconfiguration in \acp{cas},
we consider a large-scale scenario where a crowd of people is attending an event in a city
to participate in a collective activity whose computational weight is relevant, for instance
a tournament of a geo-located game similar to Ingress\footnote{\url{https://www.ingress.com/}}
or Pokémon Go\footnote{\url{https://pokemongolive.com/}}).
%
We suppose the application to be pulverised,
and its behaviour to be able to run either on the smartphones or in cloud.
%
We assume the event to start with users located in random positions in the city,
and to have a recharging station available at that place.
%
The game requires to phisically move in the city,
reach a \ac{poi} and perform some operations once there.

\cite{PianiniJOS2013}

\meta{
The simulation of this large-scale scenario should take into account several factors to be more realistic as possible:
the power consumption of the werable devices (smartphones), the power consumption of the cloud server,
and the weight of the application in terms of power dissipated by its execution.
%
The parameter described above represent the fundamental element of the power consumption model used in the simulation.
%
To be more adeherent as possible to a real consumption model of a device or cloud server,
several research were conducted to figure out real value that can be used as parameter in the simulation.
%
Nevertheless,
for our bes of knowledge,
there are no precise and established studies regarding these specific parameters.
%
For this reason,
we tried to identify likelihood parameters that could describe a plausible scenario in simulation.
%
In the following, we describe the parameters used in the simulation and the motivation behind their choice.
%
One popular metrics which relate the power consumption with the instruction is the \emph{Energy Per Instruction}
(EPI)~\cite{Grochowski2006EnergyPI} measured in $J / instruction$,
which associate the energy related to the execution of a CPU instruction.
%
From the metric introduced above, we should estimate the $EPI_{cloud}$ and $EPI_{device}$.
%
To do so, we rely our estimation based on the result obtained in~\cite{DBLP:conf/islped/ShaoB13},
were the EPI of a server CPU is calculated.
%
From the value taken from~\cite{DBLP:conf/islped/ShaoB13} we defined a discrete variability range for
$EPI_{cloud}$ equals to $300$, $30$, and $3$.
%
To estimate the $EPI_{device}$,
an intermediate step could be determine the ratio between $EPI_{cloud}$ and $EPI_{device}$,
which we define as $EPI_{ratio}$.
%
To do so we could rely on other characterizing elements:
the \emph{TDP} of each CPU and the \emph{benchmark score} of each CPU,
and for each one,
define the ratio of this two metrics: $TDP_{ratio}$ and $Benachmark_{ratio}$.
%
In this way we are identifying the power ration and performance ratio between the CPU of the device
and the CPU of the cloud.
%
The $EPI_{ratio}$ now can be define as:
$$EPI_{ratio} = \frac{TDP_{ratio}}{Benchmark_{ratio}}$$
%
Supposing to have smartphones with the \emph{Snapdragon 888} (5W TDP) as a CPU and a cloud server
with an \emph{Intel Xeon Platinum P-8124} (220W TDP), the respective benchmark results are $22,674$ and $9,362$.
%
Consequently, the $EPI_{ratio}$ is near to $18$.
%
To mitigate the uncertainty of this values we ranged the $EPI_{ratio}$ from 3 to 30.
%
The simulation consist of several scenarios in which we simulate different application load,
and consequently different discharge time of the devices.
%
To do so, we estimate the number of instruction based on
the $EPI_{device}$ and the required discharge time to simulate.
%
Given the total instruction of our application,
we repartition that value for each component executed and the relative communication cost;
in this way,
we can estimate the consumption of each component either executed in cloud or in device.
%
The power consumption is trivially determined by:
$$P = \frac{instructions * EPI}{time}$$
where \emph{time} is the time interval between two measure,
that in the simulation corresponds to the delta time between two simulation steps.
%
For what concern the cloud cost, the simulation is based on the \emph{AWS}
pricing model\footnote{\url{https://aws.amazon.com/ec2/pricing/on-demand/}}
using the \emph{m5.16xlarge} instance (which use the CPU server described above)
with a cost of \emph{\$3.584} per hour.
%
The number of instance required for running the system is calculated by
dividing the total power consumption of the cloud by the $TDP_{cloud}$.
%
The total cost of the cloud is calculated by multiplying the number of instance by the cost per hour.
}

\subsubsection{Free variables}

As follow are reported the free variables used in the evaluation:
\begin{itemize}
    \item let $n$ be the number of devices;
    \item let $t_d$ be the discharge time of the battery of the devices;
    \item let $B_l$ be the low battery threshold;
    \item let $B_h$ be the high battery threshold;
    \item let $EPI_{cloud}$ be the energy per instruction of the cloud;
    \item let $EPI_{ratio}$ be the ratio of the consumption of the cloud and the device;
\end{itemize}

\subsubsection{Metrics}

From the variables above are derived the following metrics:

\begin{itemize}
    \item let $\beta_{device}$ be the number of \emph{behaviour} executed in the device;
    \item let $\beta_{cloud}$ be the number of \emph{behaviour} executed in the cloud;
    \item let $C_{\%}$ be the average battery percentage of the devices;
    \item let $P_{devices}$ be the consumed power of the devices;
    \item let $P_{cloud}$ be the consumed power of the cloud;
    \item let $P_{total}$ be the total consumed power of the system;
    \item let $I_{cloud}$ be the number of server instances of the cloud;
    \item let $\$_{cloud}$ be the cost of the cloud;
\end{itemize}

@@

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \end{minipage}
    \caption{TODO}
    \label{fig:simulation-screenshot}   
\end{figure}

>>>>

\usepackage{cleveref}
\usepackage{color}
\usepackage{nicefrac}

@@

To show the potential benefit of automatic reconfiguration in \acp{cas},
we consider a large-scale scenario where a crowd of people is attending an event in a city
to participate in a collective activity whose computational weight is relevant, for instance
a tournament of a geo-located game similar to Ingress\footnote{\url{https://www.ingress.com/}}
or Pokémon Go\footnote{\url{https://pokemongolive.com/}}).
%
We suppose the application to be pulverised,
and its behaviour to be able to run either on the smartphones or in cloud.
%
We assume the event to start with users located in random positions in the city,
and to have a recharging station available at that place.
%
The game requires to physically move in the city,
reach a \ac{poi} and perform some operations once there.
%
We assume users with low battery to turn off the application and move to their start station to recharge the device
before rejoining the game.
%
The application is pulverised and its behaviour can execute either on the device or in the cloud.
%
We configure the framework to move the behaviour to the cloud when the battery level
(measured as a percentage of the maximum charge)
is below a threshold $\lambda$,
and to move it back to the device when the battery is charged enough to cross a threshold $\upsilon$
(stable configuration have $\upsilon{}>\lambda$,
otherwise the system continuously moves the behaviour between cloud and devices).
%
We thus indicate any configuration with $\Updownarrow^{\upsilon}_{\lambda}$,
with the exception of two cases:
$\upsilon, \lambda > 100$, forcing the behaviour to be always in the cloud, that we indicate with $\Uparrow$;
and $\upsilon, \lambda < 0$, forcing the behaviour to be always on the device, that we indicate with $\Downarrow$.
%
We are interested in the following metrics:
%
\begin{itemize}
    \item $P_{devices}$ ($kW$), the average device power consumption, a proxy for the battery life;
    \item $P_{cloud}$ ($kW$), the average power consumption of the cloud, if added to $P_{devices}$
    provides the total power consumption
    (hence, assuming a non-carbon-neutral energy mix, it is also a proxy for the carbon footprint);
    \item Distance ($km$), the total distance walked by the participants, a proxy for the \ac{qos},
    as users that need to stop and recharge stop walking;
    \item $\$_{cloud}$ (\$), the price paid to keep the required cloud instances up and running.
\end{itemize}

\subsubsection{Energy model}

\acrodef{epi}[EPI]{Energy Per Instruction}
\acrodef{tdp}[TDP]{Thermal Design Power}

We assume that the power consumption of the device is linearly dependent on the CPU usage,
and we thus decided to estimate the \ac{epi}~\cite{Grochowski2006EnergyPI}
of common smartphone ($EPI_{device}$) and server ($EPI_{cloud}$) CPUs.
%
To do so, we take the \ac{tdp} of a
Qualcomm Snapdragon 888 ($5W$)
and an
Intel Xeon Platinum P-8124 ($220W$)
and we divide it by the score the CPU obtained in the popular Passmark benchmark\footnote{\url{https://www.cpubenchmark.net/}}
($9362$ and $22674$, respectively)
obtaining an indication of the power per benchmark point
($\nicefrac{5W}{9362pts}$ and \nicefrac{220W}{22674pts} respectively).
%
We then used these ratios to estimate the relative \ac{epi} of the two CPUs,
obtaining a $EPI_{ratio}$ close to 1:18.
%
Thus,
we take the \ac{epi} estimation for the server CPU from~\cite{DBLP:conf/islped/ShaoB13},
(approximately 10J per instruction, considering 36 logical cores of our reference processor)
and we assume the \ac{epi} of the smartphone CPU to be 18 times lower.
%
Once the \acp{epi} of the two platforms are known,
we estimate the number of instructions of the pulverised components as follows:
we assume the application to be a heavy-duty game,
capable to drain the battery of a smartphone
(approximately 4500mAh in capacity, and thus, at 3.3V, 14.85Wh, 53460J)
in 6 hours of continuous usage,
which divided by the \ac{epi} of the smartphone CPU gives us the number of instructions.
%
Additionally,
we account for a variable quota of instructions that captures other activities of the devices
(screen, operating system, other applications, etc.).

\subsubsection{Cost model}
We assume the cloud to be composed by a set of Amazon \emph{AWS} instances,
specifically, \emph{m5.16xlarge} instances
(using our reference server CPU)
the \emph{AWS}
with a hourly cost of \$3.584\footnote{\url{https://aws.amazon.com/ec2/pricing/on-demand/}}
%
We estimate the number of instances required to run the pulverised components by
dividing the total power consumption of the cloud by the \ac{tdp} of the server,
assuming the CPU to be the dominant energy consumption component,
and assuming that each vCPU on AWS maps to a logical core of the underlying hardware.

\subsubsection{Implementation}
We implemented our simulations by interfacing \ourframework{}
with the Alchemist Simulator~\cite{PianiniJOS2013}
through a dedicated platfrom module.
%
We ran experiments varying the number of participants (hence, smartphones): 100, 300, and 1000.
%
For each experiment, we run a total of 10 repetitions with a different random seed;
all results are averaged over them.
%
The experiment has been open sourced\footnote{\url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}}
and the code has been archived on Zenodo~\cite{https://doi.org/10.5281/zenodo.7948801}.
%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \caption{
        A snapshot of the large-scale simulation.
        Smartphones are represented as coloured circles,
        with the color indicating their battery level
        (green when charged, red when low).
    }
    \label{fig:simulation-screenshot}
\end{figure}
%
\Cref{fig:simulation-screenshot} shows a snapshot of the simulation

@@
